Nonlinear Tidal Dissipation in Binary White Dwarfs

### 2019-03-07 proposal/FINESST/Su_FINESST_2019.tex
disclaimer

\section{Objective B\@: Tidal Heating and Binary White Dwarf Evolution
}\label{s:3}

@@

>>>>

\section{Objective B\@: Tidal Heating and White Dwarf Evolution}\label{s:3}

@@

\emph{Research performed by Cornell University is conducted as fundamental
research (basic and applied research ordinarily published and shared broadly
within the scientific community) and is therefore exempt from the requirements
of the International Traffic in Arms Regulations (ITAR) and the Export
Administration Regulations (EAR).}
